\large Taking uncertainty in word embedding bias estimation seriously ~a Bayesian approach

### 2021-07-30 presentationESSLLI21/presentationESSLLI.tex
started presentation

\documentclass[10pt,ignorenonframetext,x11names, dvipsnames, bibspacing,natbib]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{Rafal_beamerSly1}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\hypersetup{
            pdftitle={A bayesian method of cosine-based word2vec bias estimation},
            pdfauthor={Alicja Dobrzeniecka \& Rafal Urbaniak (LoPSE research group, University of Gdansk)},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\title{\large A bayesian method of cosine-based word2vec bias estimation}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak \footnotesize \newline (LoPSE
research group, University of Gdansk)}
\date{ExpSem2021, ESSLLI}

@@

\begin{frame}

\frametitle{The gist of the project}

\begin{block}{Classical probabilism in epistemology (and in
applications)}

Represent uncertainty by a single probabilistic measure (point
estimates).

\vspace{-3mm}

\begin{align*}
\pr(\mathsf{recovery}\vert \mathsf{treatment}) & = .6\\
\end{align*}

\vspace{-6mm}

@@

\begin{block}{Imprecise probabilism}

Evidence (e.g.~expert evidence) sometimes fails to warrant such
precision.

\vspace{-3mm}

\begin{align*}
\pr(\mathsf{recovery}\vert \mathsf{treatment}) & \in [.4,.6]\\
\end{align*}

\vspace{-6mm}

@@

\begin{block}{Epistemological difficulties of imprecise probabilism}

\begin{itemize}
\item
  hard to model the weight of and combine evidence.
\item
  inertia of agnosticism.
\item
  growth of uncertainty in light of new evidence.
\end{itemize}

@@

\begin{frame}{The gist of the project}

\begin{block}{My novel contribution}

\begin{itemize}
\item
  Meet the desiderata motivating imprecision.
\item
  Avoid these difficulties.
\item
  Do so by using higher-order probabilities.
\end{itemize}

\begin{center}\includegraphics[width=0.7\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-1-1} \end{center}

@@

\begin{frame}{Motivations for imprecision \large (straighforward
considerations)}

\begin{block}{Radical lack of information}

\(\pr(\mathsf{It \,\, will \,\, snow\,\, in\,\, Boston\,\, on \,\, New\,\, Year's\,\, Eve\,\, 2026}) =\)
?

@@

\begin{block}{Weight of evidence}

\begin{itemize}
\tightlist
\item
  You've seen 4/10 patients recover. \(\pr(\mathsf{recovery})=.4\)?
\end{itemize}

\pause
\vspace{-2mm}

\begin{itemize}
\tightlist
\item
  You've seen 40/100 patients recover. \(\pr(\mathsf{recovery})=.4\)?
\end{itemize}

\footnotesize (You could try to use classical statistical tools, such as
confidence intervals,\linebreak  but they have their own problems.)

@@

\begin{frame}{Motivations for imprecision \large (uniformity and
agnosticism)}

\begin{block}{Agnosticism preservation requirement}

Agnosticism about uniquely connected variables should be the same.

\vspace{-5mm}

\[X \mbox{ and } Y=X+2 \mbox{ or } Z = X^2 \,\,\, \mbox{ for $10>X>0$.}\]

@@

\begin{block}{The trouble}

\begin{center}\includegraphics[width=0.6\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-2-1} \end{center}

\vspace{-9mm}

\begin{align*}\pr(X<5) = .5 = \pr(X^2 < 25)
\end{align*}

\begin{frame}{Motivations for imprecision \large (uniformity and
agnosticism)}

\begin{block}{The trouble}

\begin{center}\includegraphics[width=0.6\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-3-1} \end{center}

\begin{frame}{Motivations for imprecision \large (expert evidence)}

\begin{block}{Weather forecasters}

\vspace{-1mm}

\begin{tabular}{ll}
Al: & $\pr(\mathsf{It \,\,  will\,\,  rain\,\,  tomorrow})=.6$\\
Bert: & $\pr(\mathsf{It \,\,  will\,\,  rain\,\,  tomorrow})=.8$
\end{tabular}

\begin{block}{Linear pooling}

\begin{align*}
\pr(\mathsf{It \,\,  will\,\,  rain\,\,  tomorrow}) & = 
\alpha \times .6 + \beta \times .8 \,\,\,\,\,  (where \,\, \alpha + \beta = 1.)
\end{align*}

\begin{block}{Mathematical impossibilities}

\begin{itemize}
\item
  Experts's agreement on independence is not preserved by linear
  pooling. ({\textbf{???}})
\item
  You can't at the same time hold the following: ({\textbf{???}})
\end{itemize}

\vspace{-7mm}

\begin{align}
\pr(A=B) & <1\\
\pr(r\vert A=a) & = a \\
\pr(r\vert B=b) & = b \\
\forall a,b \, \pr(r \vert A =a, B = b) & =  \alpha a + \beta b
\end{align}

\begin{frame}{Imprecise probabilism and the motivations}

\begin{block}{The main claim}

\justify Represent uncertainty by a set of probability measures.

\vspace{1mm} \scriptsize

({\textbf{???}}, {\textbf{???}}, {\textbf{???}}, {\textbf{???}},
{\textbf{???}}, {\textbf{???}}, {\textbf{???}}; Walley,
\protect\hyperlink{ref-walley1991statistical}{1991})

\begin{block}{Snowing in Boston?}

\vspace{-1mm}

Say, (.5,1).

\vspace{1mm} \scriptsize

({\textbf{???}})

\begin{block}{Weight of evidence?}

\vspace{-1mm}

The more evidence you have, the more narrow the interval.

\vspace{1mm} \scriptsize

({\textbf{???}}, {\textbf{???}}, {\textbf{???}})

\begin{block}{Agnosticisim?}

\vspace{-1mm}

{[}0,1{]} interval instead of a single uniform distribution.

\begin{block}{Multiple sources?}

\vspace{-1mm}

Just put all those probabilities in one set.

\begin{frame}{Epistemological challenges}

\begin{block}{Radical uncertainty and weight}

Say one experiment observed 40/100 and another 8/15 recoveries.

Simply putting the frequencies in a set won't do justice to the
evidence.

\scriptsize  \vspace{1mm}

({\textbf{???}})

\begin{block}{Dilation}

\justify Whenever your roomate goes to the track he flips a fair coin.
If it comes up heads he bets on Speedy. Otherwise he places no bets. He
comes home from the track grinning. You're now more uncertain about
\(\pr(\mathsf{heads})\) than before.

\scriptsize

\vspace{1mm} ({\textbf{???}}, {\textbf{???}}, {\textbf{???}},
{\textbf{???}}, {\textbf{???}}, {\textbf{???}}; Walley,
\protect\hyperlink{ref-walley1991statistical}{1991})

\begin{frame}{Epistemological challenges}

\begin{block}{Belief inertia}

Say you're fully agnostic about \(H\): \(P(H) = [0,1]\).

\begin{center}

\begin{center}\includegraphics[width=0.7\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\end{center}

Then \(\pr(H \vert E) =[0,1]\), no matter what the evidence says.

\vspace{1mm} \scriptsize

({\textbf{???}},({\textbf{???}}), {\textbf{???}}, {\textbf{???}},
{\textbf{???}}, {\textbf{???}})

\begin{frame}{Epistemological challenges}

\begin{block}{Mystery coins}

\begin{itemize}
\tightlist
\item
  A fair draw of one of two biased coins, with biases \(.4, and .6\).
\end{itemize}

\begin{itemize}
\tightlist
\item
  Imprecise reaction: \(\{.4, .6\}\).
\end{itemize}

\begin{itemize}
\tightlist
\item
  Precise probabilism: expected bias of \(.5\).
\end{itemize}

\begin{block}{Question}

As far as accuracy is concerned, why prefer the imprecise way?

Say the actual bias is .4. A first stab:

\vspace{-3mm}

\begin{align*}
\mathsf{inaccuracy(imprecise)} & = \frac{0 + .2}{2} = .1\\
\mathsf{inaccuracy(precise)} & =  .1\\
\end{align*}

\vspace{-5mm} \scriptsize

({\textbf{???}}, {\textbf{???}}; Schoenfield,
\protect\hyperlink{ref-schoenfield2017AccuracyRationalityImprecise}{2017})

\begin{frame}{Higher-order approach}

\begin{block}{The mystery coin with \((.2,.8)\) and 1 head in five
tosses}

\begin{center}\includegraphics[width=0.9\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-5-1} \end{center}

\begin{frame}{Higher-order approach}

\begin{block}{Two experts, uniform prior}

\begin{center}\includegraphics[width=0.9\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-6-1} \end{center}

\begin{frame}{The key conjecture}

\begin{block}{With higher-order methods, it will be possible to:}

\begin{itemize}
\item
  match the representation of uncertainty with the evidence,
\item
  combine various sources of uncertainty without running into the known
  problems,
\item
  use existing mathematics to make sense of accuracy in such contexts,
\item
  capture reasoning with radical uncertainty without dilation and belief
  inertia.
\end{itemize}

\begin{frame}{Tasks (discussion)}

\begin{itemize}
\tightlist
\item
  Relate this representation to weight of evidence.
\end{itemize}

\begin{itemize}
\item
  Go beyond grid approximation and beta representation.
\item
  Represent agnosticism so that:

  \begin{itemize}
  \item
    agnosticism preservation holds, and
  \item
    inertia fails.
  \end{itemize}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Represent opinion aggregation more generally, compare to known
  limitations and features of already studied opinion pooling methods.
\end{itemize}

\begin{itemize}
\tightlist
\item
  Investigate dilation-like phenomena in this context.
\end{itemize}

\begin{itemize}
\tightlist
\item
  Study known distance functions between probabilistic measures as
  candidates for key elements of accuracy measures.
\end{itemize}

\begin{itemize}
\tightlist
\item
  Explain away the apparent contrast between evidence-grounding and
  accuracy considerations (Easwaran \& Fitelson,
  \protect\hyperlink{ref-easwaranAndFitelson2015}{2015}).
\end{itemize}

\begin{center}
\Large Thank you for your attention!
\end{center}

@@

\hypertarget{refs}{}
\hypertarget{ref-easwaranAndFitelson2015}{}
Easwaran, K., \& Fitelson, B. (2015). Accuracy, coherence, and evidence.
In T. S. Gendler \& J. Hawthorne (Eds.), \emph{Oxford studies in
epistemology} (Vol. 5). Oxford University Press.

\hypertarget{ref-schoenfield2017AccuracyRationalityImprecise}{}
Schoenfield, M. (2017). The Accuracy and Rationality of Imprecise
Credences: The Accuracy and Rationality of Imprecise Credences.
\emph{Noûs}, \emph{51}(4), 667--685.
\url{https://doi.org/10.1111/nous.12105}

\hypertarget{ref-walley1991statistical}{}
Walley, P. (1991). \emph{Statistical reasoning with imprecise
probabilities}. Chapman; Hall London.

>>>>

\documentclass[10pt,ignorenonframetext,x11names, dvipsnames, bibspacing,natbib]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{Rafal_beamerSly1}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\hypersetup{
            pdftitle={Taking uncertainty in word embedding bias estimation seriously ~a Bayesian approach},
            pdfauthor={Alicja Dobrzeniecka \& Rafal Urbaniak (LoPSE research group, University of Gdansk)},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{caption}
% These lines are needed to make table captions work with longtable:
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother

@@

\title{\large Taking uncertainty in word embedding bias estimation seriously ~a
Bayesian approach}
\author{Alicja Dobrzeniecka \& Rafal Urbaniak \footnotesize \newline (LoPSE
research group, University of Gdansk)}
\date{ExpSem2021, ESSLLI}

@@

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Word embeddings}

\begin{itemize}
\item
  Representation of words (or words in contexts) with vectors of real
  numbers
\item
  Built to predict the probability of co-occurence
\end{itemize}

\begin{longtable}[]{@{}llllll@{}}
\toprule
word & 1 & 2 & 3 & 4 & \ldots{}\tabularnewline
\midrule
\endhead
woman & 0.456 & 0.267 & 0.675 & 0.131 & \ldots{}\tabularnewline
man & 0.451 & 0.897 & 0.472 & 0.088 & \ldots{}\tabularnewline
\bottomrule
\end{longtable}

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Cosine similarity \& distance}

\begin{align} \tag{Sim}
\mathsf{cosineSimilarity}(A,B) & = \frac{A \cdot B}{\vert \vert A \vert \vert \,\vert \vert B \vert \vert}
\\
\tag{Distance}
\mathsf{cosineDistance}(A,B) &  = 1 - \mathsf{cosineSimilarity}(A,B)
\end{align}

\begin{itemize}
\item
  Geometric interpretation: direction (not length)
\item
  \(\mathsf{cosineDistance}\in (0, 2)\)
\item
  Naive interpretation: proximity corresponds to semantic similarity
  (e.g.~no triangle inequality)
\end{itemize}

\begin{frame}{Cosine-based measures of bias}

\begin{block}{The worry}

In the learning process these models can learn implicit biases that
reflect harmful stereotypical thinking

@@

\begin{block}{Cosine-based bias: basic intuition}

Words belonging to an intuitively harmful stereotype are cosine-close to
each other

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Stereotypical lists}

\begin{itemize}
\item
  feminine occupations: ``homemaker'', ``nurse'', ``receptionist'',
  ``librarian'', etc.
\item
  masculine occupations: ``maestro'', ``captain'', ``architect'', etc.
\end{itemize}

\normalsize

\begin{block}{Visual example}

\vspace{1mm} \footnotesize

\begin{center}\includegraphics[width=0.6\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-1-1} \end{center}

\normalsize

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Example: direct bias}

\begin{itemize}
\tightlist
\item
  The gender bias of a word \(w\) is its projection on the gender
  direction
  \(\vec{w} \cdot (\overrightarrow{he} - \overrightarrow{she})\)
\end{itemize}

\begin{itemize}
\tightlist
\item
  Given the (ideally) gender neutral words \(N\) and the gender
  direction \(g\) the direct gender bias is: 
\end{itemize}

\begin{align}
\mathsf{directBias_c(N,g)} & = \frac{\sum_{w\in N}\vert \mathsf{cos}(\vec{w},g)\vert^c}{\vert N \vert }
\end{align}

(Bolukbasi, Chang, Zou, Saligrama, \& Kalai,
\protect\hyperlink{ref-Bolukbasi2016Man}{2016})

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Example: Word Embedding Association Test (WEAT)}

\begin{align*}
s(t,A,B) & = \frac{\sum_{a\in A}f(t,a)}{\vert A\vert} - \frac{\sum_{b\in B}f(t,b)}{\vert B\vert}
\\
WEAT(A,B) & = \frac{
\mu\left(\{s(x,A,B)\}_{x\in X}\right) -\mu\left(\{s(y,A,B)\}_{y\in Y}\right) 
}{
\sigma\left(\{s(w,A,B)\}_{w\in X\cup Y}\right)
}
\end{align*}

\begin{itemize}
\item
  \(t\) is a term, \(A, B\) are sets of stereotype attribute words, \$X,
  \(Y\) are protected group words
\item
  For instance, \(X\) might be a set of male names, \(Y\) a set of
  female names, \(A\) might contain stereotypically male-related career
  words, and \(B\) stereotypically female-related family words
\item
  \(s\)-values are used as datapoints in statistical significance tests
\end{itemize}

(Caliskan, Bryson, \& Narayanan,
\protect\hyperlink{ref-Caliskan2017semanticsBiases}{2017}) with
extensions in (Lauscher \& Glavas,
\protect\hyperlink{ref-Lauscher2019multidimensional}{2019}) and
applications in (Garg, Schiebinger, Jurafsky, \& Zou,
\protect\hyperlink{ref-Garg2018years}{2018})

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}

\begin{align*}
S(t_i, A_j) & = \frac{1}{\vert A_j\vert}\sum_{a\in A_j}\mathsf{cos}(t,a) \\
MAC(T,A) & = \frac{1}{\vert T \vert \,\vert A\vert}\sum_{t_i \in T }\sum_{A_j \in A} S(t_i,A_j)
\end{align*}

\begin{itemize}
\item
  \(T = \{t_1, \dots, t_k\}\) is a class of protected words
\item
  each \(A_j\in A\) is a set of attributes stereotypically associated
  with a protected word
\end{itemize}

\begin{itemize}
\tightlist
\item
  The t-tests they employ are run on average cosines used to calculate
  MAC
\end{itemize}

(Manzini, Lim, Tsvetkov, \& Black,
\protect\hyperlink{ref-Manzini2019blackToCriminal}{2019})

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Our main target: Mean Average Cosine Similarity (MAC)}

\begin{table}

\caption{\label{tab:religionTableHeadEarly}Rows the religion dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrr}
\toprule
protectedWord & wordToCompare & cosineDistance & cosineSimilarity\\
\midrule
jew & greedy & 0.6947042 & 0.3052958\\
rabbi & greedy & 1.0306175 & -0.0306175\\
rabbi & conservative & 0.7175887 & 0.2824113\\
christian & uneducated & 0.5081939 & 0.4918061\\
christianity & cheap & 1.2816164 & -0.2816164\\
muslim & terrorist & 0.2726106 & 0.7273894\\
\bottomrule
\end{tabular}}
\end{table}

\normalsize

\begin{frame}{Cosine-based measures of bias}

\begin{block}{Known challenges}

\begin{itemize}
\item
  Gender-direction might be an indicator of bias, but is insufficient.
  After debiasing other non-gendered words can remain in biased
  relations (Gonen \& Goldberg,
  \protect\hyperlink{ref-Gonen2019lipstick}{2019})
\item
  Methods which involve analogies and their evaluations by human users
  on Mechanical Turk are unreliable (Nissim, Noord, \& Goot,
  \protect\hyperlink{ref-Nissim2020fair}{2020})
\end{itemize}

\begin{frame}{Some methodological problems}

\begin{block}{Word list choice is unprincipled}

We run with it for comparison

@@

\begin{block}{No design considerations to sample size}

We investigate the uncertainty that arises from raw sample sizes

@@

\begin{frame}{Some methodological problems}

\begin{block}{No word class distinction and no control group}

We make the subclasses clear, add human neutral predicates and neutral
predicates for control

\begin{table}

\caption{\label{tab:religionTableHeadLate}Rows from extended religion dataset.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllrrl}
\toprule
protectedWord & wordToCompare & wordClass & cosineDistance & cosineSimilarity & connection\\
\midrule
torah & hairy & jewish & 1.170 & -0.170 & associated\\
christian & dirty & muslim & 0.949 & 0.051 & different\\
judaism & cheap & jewish & 1.232 & -0.232 & associated\\
christianity & familial & christian & 0.645 & 0.355 & associated\\
mosque & approve & neutral & 0.995 & 0.005 & none\\
imam & carry & human & 0.993 & 0.007 & human\\
mosque & merging & neutral & 0.868 & 0.132 & none\\
muslim & nationalized & neutral & 0.870 & 0.130 & none\\
\bottomrule
\end{tabular}}
\end{table}

\normalsize

@@

\begin{frame}{Some methodological problems}

\begin{block}{Outliers and surprisingly dissimilar words}

We study those by visualizations and uncertainty estimates

@@

\begin{block}{No principled interpretation}

\begin{longtable}[]{@{}ll@{}}
\toprule
Religion Debiasing & MAC (distance)\tabularnewline
\midrule
\endhead
Biased & 0.859\tabularnewline
Hard Debiased & 0.934\tabularnewline
Soft Debiased (\(\lambda\) = 0.2) & 0.894\tabularnewline
\bottomrule
\end{longtable}

What values are sufficient for the presence of bias and what differences
are sign of real improvement? Low \(p\)-values are not high effect
indicators!

We compare HPDIs.

@@

\begin{frame}{The problem with pre-averaging}

\begin{frame}{Bayesian estimation}

\begin{center}\includegraphics[width=1.05\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-2-1} \end{center}

\begin{frame}{Bayesian estimation}

\begin{center}\includegraphics[width=1.05\linewidth]{presentationESSLLI_files/figure-beamer/unnamed-chunk-3-1} \end{center}

\begin{frame}{Effects of debiasing}

\begin{block}{Further work}

\begin{itemize}
\tightlist
\item
  downstream tasks
\end{itemize}

@@

@@

\hypertarget{refs}{}
\hypertarget{ref-Bolukbasi2016Man}{}
Bolukbasi, T., Chang, K., Zou, J. Y., Saligrama, V., \& Kalai, A.
(2016). Man is to computer programmer as woman is to homemaker?
Debiasing word embeddings. \emph{CoRR}, \emph{abs/1607.06520}. Retrieved
from \url{http://arxiv.org/abs/1607.06520}

\hypertarget{ref-Caliskan2017semanticsBiases}{}
Caliskan, A., Bryson, J. J., \& Narayanan, A. (2017). Semantics derived
automatically from language corpora contain human-like biases.
\emph{Science}, \emph{356}(6334), 183--186.
\url{https://doi.org/10.1126/science.aal4230}

\hypertarget{ref-Garg2018years}{}
Garg, N., Schiebinger, L., Jurafsky, D., \& Zou, J. (2018). Word
embeddings quantify 100 years of gender and ethnic stereotypes.
\emph{Proceedings of the National Academy of Sciences}, \emph{115}(16),
E3635--E3644. \url{https://doi.org/10.1073/pnas.1720347115}

\hypertarget{ref-Gonen2019lipstick}{}
Gonen, H., \& Goldberg, Y. (2019). Lipstick on a pig: Debiasing methods
cover up systematic gender biases in word embeddings but do not remove
them. \emph{Proceedings of the 2019 Conference of the North American
Chapter of the Association for Computational Linguistics: Human Language
Technologies, Volume 1 (Long and Short Papers)}, 609--614. Minneapolis,
Minnesota: Association for Computational Linguistics.
\url{https://doi.org/10.18653/v1/N19-1061}

\hypertarget{ref-Lauscher2019multidimensional}{}
Lauscher, A., \& Glavas, G. (2019). Are we consistently biased?
Multidimensional analysis of biases in distributional word vectors.
\emph{CoRR}, \emph{abs/1904.11783}. Retrieved from
\url{http://arxiv.org/abs/1904.11783}

\hypertarget{ref-Manzini2019blackToCriminal}{}
Manzini, T., Lim, Y. C., Tsvetkov, Y., \& Black, A. W. (2019).
\emph{Black is to criminal as caucasian is to police: Detecting and
removing multiclass bias in word embeddings}.

\hypertarget{ref-Nissim2020fair}{}
Nissim, M., Noord, R. van, \& Goot, R. van der. (2020). Fair is better
than sensational: Man is to doctor as woman is to doctor.
\emph{Computational Linguistics}, \emph{46}(2), 487--497.
\url{https://doi.org/10.1162/coli_a_00379}
